% Copyright (C) Dean Gadberry - All Rights Reserved
% Unauthorized copying of this file, via any medium is strictly prohibd
% Proprietary and confidential
% Written by Dean Gadberry <dean@deangadberry.com>, 2023

\documentclass[12pt,a4paper,english]{article}
\usepackage{helvet}         % set font to helvetica
\renewcommand{\familydefault}{\sfdefault}
\usepackage{sectsty}        % allow redefinition of section command formatting
    \allsectionsfont{\normalsize}
\usepackage[centering,noheadfoot,margin=1in]{geometry}
\usepackage{lipsum}
\setlength{\parindent}{0em}
\usepackage{parskip}
\usepackage{hanging}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan}

% https://tex.stackexchange.com/questions/30720/footnote-without-a-marker
\newcommand\blindfootnote[1]{
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}
  \addtocounter{footnote}{-1}
  \endgroup
}
\AtEndDocument{\blindfootnote{\textrm{This document proudly made using \LaTeX{}}}}

\begin{document}
\begin{flushleft}

Dean Gadberry\\
1947 Colorado Blvd APT C\\
Denton, TX 76205\\
469-420-0771

\par

To whom it may concern,

I am writing to inform you of my interest in your job offering: Financial Operations Associate. It is my pleasure to tell you that you may finish your search for a qualified, driven individual to fulfill this role. I recently viewed this listing on indeed.com, and did not hesitate to apply immediately.

I am currently working with Classy Closets of DFW in an accounts payable/receivable \& payroll position. I am intimately involved in the operations of this small business. Within this role, I have led our accounting team in compiling standard operating procedures. I have written over 200 pages of information regarding our QuickBooks standards, Customer Relations Management, and Record Keeping. My skills are esteemed by my colleages and managers. 

I am interested in joining a company which values, not only my skills, but also my integrity, inclusivity, and excellence; a company which is commited to the success of their community. 

I am excited to indulge in the opportunity to thrive on providing exceptional client services while living a true work-life balance.

I look forward to hearing from you.

\hfill\break
\hfill\break
\hfill\break
Sincerely,

Dean Gadberry \\
\href{https://www.deangadberry.com}{\texttt{DeanGadberry.com}}\\
\href{mailto:contact@deangadberry.com}{\texttt{contact@DeanGadberry.com}}\\

\end{flushleft}
\end{document}
