% Copyright (C) Dean Gadberry - All Rights Reserved
% Unauthorized copying of this file, via any medium is strictly prohibd
% Proprietary and confidential
% Written by Dean Gadberry <dean@deangadberry.com>, 2023

\documentclass[12pt,a4paper,english]{article}
\usepackage{helvet}         % set font to helvetica
\renewcommand{\familydefault}{\sfdefault}
\usepackage{sectsty}        % allow redefinition of section command formatting
    \allsectionsfont{\normalsize}
\usepackage[centering,noheadfoot,margin=1in]{geometry}
\usepackage{lipsum}
\setlength{\parindent}{0em}
\usepackage{parskip}
\usepackage{hanging}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan}
\usepackage{amsmath}
\usepackage{esvect}
\usepackage{currfile}
\setcounter{secnumdepth}{0}

\newcommand{\degree}[1]{${#1}^\circ$}

% https://tex.stackexchange.com/questions/30720/footnote-without-a-marker
\newcommand\blindfootnote[1]{
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}
  \addtocounter{footnote}{-1}
  \endgroup
}
\AtEndDocument{\blindfootnote{\textrm{This document proudly made using \LaTeX{}}}}

\begin{document}
\begin{flushright}
  Dean Gadberry

  NCTC PHYS 2425

  \today
\end{flushright}
\begin{center}
  {\large Chapter 3 Homework}
\end{center}
\begin{flushleft}
  \section*{QUESTIONS}
  \hrule
  \subsection{10. Does the odometer of a car measure a scalar or a vector quantity? What about the speedometer?}
  The odometer of a car measures a scalar quantity. The speedometer also measures a scalar quantity.
  \subsection{16. A projectile is launched at an upward angle of \degree{30} to the horizontal with a speed of 30m/s. How does the horizontal component of its velocity 1.0s after launch compare with its horizontal component of velocity 2.0s after launch, ignoring air resistance? Explain.}
  The projectile will be farther away after 2 seconds than it is at 1 second. It's velocity in the horizontal direction will not change, though, because the force of gravity will only have an effect on the vertical velocity.
  \subsection{17. A projectile has the least speed at what point in its path?}
  A projectile has the least speed at the apex of it's climb and the termination of it's path.
  \subsection{19. A person sitting in an enclosed train car, moving at a constant velocity, throws a ball straight up into the air in her reference frame.}
  \subsubsection{(a) Where does the ball land?}
  The ball lands where it started on the train.
  \subsubsection{(b) Where does the ball land if the car accelerates?}
  The ball lands in the negative x direction in relation to it's starting position in the train's reference frame.
  \subsubsection{(c) Where does the ball land if the car deccelerates?}
  In the train's reference frame, the ball will land +x from where it started.
  \subsubsection{(d) Where does the ball land if the car rounds a curve?}
  In this case, the ball will land offset by some value of z and likely an offset of x as well.
  \subsubsection{(e) Where does the ball land if the car moves with constant velocity but is open to the air?}
  Assuming air resistance, the ball will land behind it's starting position, that is the -x direction.
  \section*{MISCONCEPTION QUESTIONS}
  \hrule
  \subsection{4. Which of the following equations correctly expresses the relation beween vectors $\vv{A}, \vv{B},$ and $\vv{C},$ shown in Fig 3-36?}
  (b)\vv{B}=\vv{A}+\vv{C}
  \subsection{6. A bullet fired horizontally from a rifle begins to fall}
  (a) as soon as it leaves the barrel
  \subsection{9. Two balls having different speeds roll off the edge of a horizontal table at the same time. Which hits the floor sooner?}
  (c) Both the same.
  \subsection{10. You are riding in an enclosed train car moving at 90km/h. If you throw a baseball straight up, where will the baseball land?}
  (c) In your hand.
  \subsection{11. Which of the three kicks in Fig. 3-38 is in th eair for the longest time? They all reach the same maximum height $h$. Ignore air resistance.}
  (c)
  \subsection{13. A hunter is aiming horizontally at a monkey who is sitting in a tree. the monkey is so terrified when it sees the gun that it falls off the tree. At that very instant, the hunter pulls the trigger. What will happen?}
  (d) It depends on how far the hunter is from the monkey.
  \pagebreak
  \section*{PROBLEMS}
  \hrule
  \subsection{1. A car is driven 245 km west and then 118 km southwest (\degree{45}). What is the displacement of the car from the point of origin (magnitude and direction)? Draw a diagram.}
  \[
  \vv{a}_x=-245km
  \vv{b}_x=83.44
  \vv{b}_y=83.44
\]
  \subsection{2. If $V_x=9.40$ units and $V_y=-6.80$ units, determine the magnitude and direction of \vv{V}}
  \[
    tan^{-1}(\frac{9.40}{-6.80})=-54.1^\circ
  \]
  \[
    V_r=\sqrt{9.40^2+6.80^2}=11.6
  \]
    $\vv{V}=11.6 \angle 54.1^\circ$ south of east
  \subsection{8. An airplane is traveling 815km/h in a direction \degree{41.5} west of north.}
  \subsubsection{(a) Find the components of the velocity vector in the northerly and westerly directions.}
  \[
    cos(41.5)=\frac{y}{815} \implies y=815(cos(41.5))=610.4
  \]
  610.4 km/h North
  \[
    sin(41.5)=\frac{x}{815} \implies x=815(sin(41.5)) = 540.0
  \]
  540.0 km/h West
  \subsubsection{(b) How far north and how far west has the plane traveled after 1.75h?}
  \[
    610.4\times 1.75=1068.2
  \]
1068.2 km North
\[
  540.0\times 1.75=945
\]
945 km West
  \subsection{9. The summit of a mountain, 2450 m above base camp, is measured on a map to be 4580 m horizontally from the camp in a direction \degree{38.4} west of north. What are the components of the displacement vector from camp to summit? What is its magnitude? Choose the x axis east, y axis north, and z axis up.}
  \[
    sin38.4=\frac{x}{4580}\implies
    x=4580sin38.4\implies
    x=2844.9m
  \]
  \[
    cos38.4=\frac{y}{4580}\implies
    y=4580cos38.4\implies
    y=3589.3m
  \]
  z: 2450m

  magnitude: 4580m
  \subsection{10. Three vectors magnitudes are given in arbitrary units. Determine the sum of the three vectors. Give the resultant in terms of}
  \subsubsection{(a) components}
  \begin{tabular}{c|ccccc}
    Vector & Resultant & Degree & Calculations & \vv{V}_x & \vv{V}_y \\
    \hline
    \\
    \vv{A} & 42.0 & 28.0 
           & \vv{A}_x=42cos(28) 
           & 37.08\\
    _&&&\vv{A}_y=42sin(28) 
     & & 19.72\\
    \\
    \vv{B} & 29.7 & 56.0 
           & \vv{B}_x=29.7cos(56.0)
           & -16.61\\
    _&&&\vv{B}_y=29.7sin(56.0) 
     & & 24.62\\
    \\
    \vv{C} & 31.0 &
           &&&-31.0\\
    _&\\
    \hline
    \hline
    \\
    \vv{D} &&&\vv{D}_x=37.08-16.61&20.47\\
           &&&\vv{D}_y=19.72+24.62-31.0&&13.34\\
           &&33.09&$tan^{-1}(\frac{13.34}{20.47})$\\
           &24.43&&\vv{D}_R=\sqrt{(13.34)^2+(20.47)^2}\\
    \hline
  \end{tabular}
  \subsubsection{(b) magnitude and angle with the +x axis}
  \vv{D}=24.43\angle 33.09^\circ
  \subsection{32. A tiger leaps horizontally from a 7.5-m-high rock with a speed of 3.0m/s. How far from the base of the rock will he land?}
  \[
    \Delta y=v_{0y}t-\frac{1}{2}gt^2 \implies -7.5=-4.9t^2\implies
    \sqrt{\frac{-7.5}{-4.9}}=t=1.24s
  \]
  \[
    \Delta x =v_{x0}t\implies
    \Delta x=3.0(1.24)\implies
    \Delta x=3.72m
  \]
  \subsection{34. A ball is thrown horizontally from the roof of a building 7.5m tall and lands 9.5m from the base. What was the ball's initial speed?}
  \[
    \Delta y=v_{0y}t-\frac{1}{2}gt^2 \implies 
    -7.5=-4.9t^2\implies
    \sqrt{\frac{-7.5}{-4.9}}=t=1.24s
  \]
  \[
  v_{0x}=\frac{\Delta x}{t}\implies
  v_{0x}=\frac{9.5}{1.24}\implies
  v_{0x}=7.66m/s
  \]
  \subsection{36. A football is kicked at ground level with a speed of 18.0m/s at an angle of \degree{31.0} to the horizontal. How much later does it hit the ground?}
\[
  R=\frac{v_0^2sin2\theta}{g}\implies
  R=\frac{18.0sin(62)}{9.8}\implies
  R=1.62m
\]
\[
  \Delta x=v_{0x}t\implies
  t=\frac{\Delta x}{v_{0x}}\implies
  t=\frac{1.62}{18.0}\implies
  t=0.09s
\]
  \subsection{47. A rescue plane wants to drop supplies to isolated mountain climbers on a rocky ridge 265m below. If the plane is traveling horizontally with a speed of 125km/h, how far in advance of the recipients (horizontal distance) must the goods be dropped?}
  Given:
\[
  \Delta y = -265m
\]
  \[
  v_{x0} =34.72m/s=\biggr( \frac{125km}{h} \times \frac{1h}{3600s}\times \frac{1000m}{1km}\biggr)
\]

Find: \Delta x\\
\[
  \Delta y=v_{y0}t-\frac{1}{2}gt^2\implies
  -265=-4.9t^2\implies
  t=\sqrt{\frac{-265}{-4.9}}\implies
  t=7.354
\]
\[
  \Delta x=v_{x0}t\implies
  \Delta x=(34.72m/s)(7.354s)\implies
  \Delta x=255.3m
\]
\end{flushleft}
\end{document}
